% CV / Resume: Alvin Kerber
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Curriculum Vitae template by Ezra Miller
%  29 September 2007
%
% To anyone downloading this file:
%
% If you got this file from someone other than Ezra Miller, then there
% might be a better version available directly from Ezra's homepage;
% just type Ezra Miller into Google and you should be able to find it.
%
% You may use this file freely as a template for your own CV, or for
% any other purpose, but please leave these lines and those above them
% in the file.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\documentclass[10pt,letterpaper]{article}
\usepackage{lmodern}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[margin=1in]{geometry}
\usepackage{url}

% Block comments for old content
\newcommand{\archive}[1]{}

% \newcommand{\marginlabel}[1]{\smallskip\noindent{\large{\textsf{\textbf{#1}}}}\smallskip}
\newcommand{\marginlabel}[1]{\smallskip\noindent{\large{\textsf{\textbf{#1}}}}}

\newcommand{\dates}[1]{\item[#1\hfill]}

% <year>-<year>  <COMPANY> --- <Title>
\newcommand{\jobhead}[3]{{\dates{#1}{\bf #2} --- {#3}}}

% <year>-<year>  <COMPANY> --- <Title>
% \newcommand{\jobsubhead}[2]{{\dates{\it (#1)}{\it #2}}}
% \newcommand{\jobsubhead}[2]{{{\it #2}}}
\newcommand{\jobsubhead}[2]{{{\it #2 (#1)}}}

% <year>-<year>  <Title> ....................................... /<Company>/
%\newcommand{\jobhead}[3]{\dates{#1}{\bf #2}\hfill{\it #3}}

% <year>-<year>  <Project>
\newcommand{\projecthead}[2]{{\dates{#1}{\bf #2}}}

\newenvironment{jobs}
  {\leftmargini=24.1mm%
   \begin{list}%
    {}
    {\setlength\labelwidth{22mm}\itemsep=1.5mm}}
  {\end{list}}

% Compact lists with cool triangles!
\setlist{nosep}
\setlist[1]{\labelindent=\parindent}
\setlist[itemize]{label=\tiny\raise2.25pt\hbox{$\blacktriangleright$}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\thispagestyle{empty}

\noindent\begin{tabular}[t]{@{}l}
\url{www.alvinkerber.net} \\
\url{github.com/akerber47/}
\end{tabular}
\hfill
\begin{tabular}[t]{c}
\raisebox{-2.0ex}{\bfseries \LARGE A\large LVIN \LARGE K\large ERBER}
\end{tabular}
\hfill
\begin{tabular}[t]{r@{}}
\verb!+!1\,\,510\,\,374\,\,8997 \\
\url{alvin@alvinkerber.net}
\end{tabular}

\vspace{1ex}
\hrule
\vspace{1ex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\marginlabel{Employment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{jobs}

\jobhead{2017\,--\,present} {Facebook}{Research Scientist}

\jobsubhead{2019\,--\,present}{Instagram Ads Ranking, Core Optimization}

\begin{itemize}
\item Individually delivered features, models, and ranking stack treatments that improved
	overall IG ads revenue by 1\% or more each year.

\item Applied cutting-edge ML techniques in clustering, graph learning, representation learning,
	content understanding, and Poincare embedding / hyperbolic manifold regression.

\item Responsible for success of data mining / feature eng area throughout IG ads. Mentored, steered
	direction, and helped unblock all feature projects across the org.
	Reviewed all proposed features for ranking impact and return on infra cost.

\item Led refactoring and migration of complex legacy IG feature infrastructure,
	enabling 10\verb!+! follow-up feature eng projects.
	Influenced org-level planning and priorities
	in the separate FB ads infra org. Debugged
	performnce regressions and migration blockers requiring multi-week investigation.

\item Responsible for quality, stability, and resource consumption of data
	pipeline codebase throughout IG ads. Established new 10-member data oncall across the
	org, created expectations and runbook, and built org-wide support structure
	to ensure oncall success.

\end{itemize}

\jobsubhead{2017\,--\,2019}{ML for Developer Observability}
\begin{itemize}

\item Shipped 3 green-field internal tools to provide internal situational
	recommendations and insights to engineers based on previous
	engineers' behavior. Recommendations were also integrated into company-wide oncall hub and
	internal search tools.

\item Owned and drove ML direction, modeling approaches, and end-to-end
	recommendation system architecture on team of 4 engineers.

\item Used collaborative filtering, clustering, heuristics, and semi-supervised learning
	to extract insights from large-scale unlabeled
	employee behavior data.


\end{itemize}

\archive{

\item Studied internal engineer activity data to build models that make
	predictions of employee behavior and recommendations to help people be
	more productive.

\item Applied cutting-edge ML techniques including context-based embedding
	features, deep neural networks, and semi-supervised training to attack
	unsolved research problems arising from noise and lack of labels
	in employee activity data at company-wide scale (over 10M
	human activity events per day).

\item Designed and implemented two end-to-end internal tools to provide
	suggestions directly to engineers, including data pipelines, ML models,
	and back- and front-end web code.

\item Suggestions are currently visited by 200\verb!+! engineers each day at
	high-visibility integration points (internal search bar and on-call
	dashboard).

\item Taught seminar for 8\verb!+! teammates on various machine learning and
	inference topics.

}

\archive{
\jobhead{2011\,--\,2017} {University of California, Berkeley}{Graduate Student
Researcher, Mathematics}
\begin{itemize}

\item Solved the quasi-Fuchsian surface subgroup conjecture for books of
	I-bundles. \archive{Currently preparing paper for submission.}

\item Researched multiple open problems in 3-manifold topology, including
	pseudo-Anosov conjugacy, harmonic maps to trees, and quasi-Fuchsian
	surface subgroups.

\end{itemize}
}

\jobhead{2015\,--\,2016} {Delphix}{Member of Technical Staff} \begin{itemize}

\archive{
\item Designed and implemented features and
stability improvements for the Oracle platform.
}

\item Owned and drove incremental development, production stability, and
	modernization for the Provisioning component of Delphix's Oracle
	data platform, used in 50\verb!+! Fortune 500
	companies' daily workflows and required for over 60\% of company
	revenue.

\archive{
\item Fixed 5\verb!+! deal-breaking escalated issues, helping retain
	\$200,000\verb!+!/yr customers.
}

\end{itemize}

\jobhead{2015} {Delphix}{Software Engineering Intern}

\archive{
\begin{itemize}
\item Implemented new snapshot-metadata feature across Delphix
data platforms.
\end{itemize}
}

\jobhead{2014}
{Google}{Software Engineering Intern, Machine Learning}

\archive{
\begin{itemize}
\item Built user-level ML model to estimate malicious Google\verb!+! account rate and
	surface additional suspicious accounts for manual review.
\end{itemize}
}

\archive{
\item Over $95\%$ classification accuracy and $75\%$ sensitivity on
test data.


\item Computed estimate of how many malicious accounts are active on G\verb!+!.

\item Selected input features and wrote large-scale queries and scripts on
Google technologies (Flume, Dremel) to gather and process data
\item Implemented Python scripts to process general CSV data for input to model
\item Model slated for production use, where it will be the first broad
classifier to flag and prioritize suspicious accounts
for further review, saving account reviewer man-hours.
}

\archive{ \jobhead{2012}{Instructor}{Berkeley Math Dept} \begin{itemize} \item
	Created syllabus, lesson plans, and exams for 35-student summer
	calculus course.  \item Taught 10 hours of lectures, groupwork, and
discussion each week.  \end{itemize} }

\archive{
\jobhead{2008\,--\,2015}{University of California, Berkeley \& Brown
University}{Teaching Assistant}
\begin{itemize}
\archive{\item Taught discussions and labs, graded,
and wrote solutions.}
\item Calculus, Multivariable Calculus, Linear Algebra, Numerical Analysis,
Discrete Math.
\item Accelerated Introduction to CS, Operating Systems, Operating Systems Lab.
\end{itemize}
}

% PAST JOBS
\archive{
\jobhead{2010\,--\,2011}
{Course Developer and TA, Operating Systems}{Brown CS Dept}
\begin{itemize}
\item Ported OS used for teaching from paravirtualized platform to more
realistic full hardware emulator.
\item Refactored and ported 25,000 lines of kernel C and x86 assembly code.
\item Implemented new
scheduler, memory management system, dynamic linker/loader,
interrupt handlers,
and drivers (keyboard, display, serial, hard disk).
\item Eliminated frequent platform crashes and sped up student build/deploy
time by 10x.
\end{itemize}

\jobhead{2010\,--\,2011}{Head Lab Consultant}{Brown CS Dept}
\begin{itemize}
\item Hired, trained, and supervised 15 student lab employees.
\item Rewrote and streamlined scripts for employee shift scheduling and
hours logging.
\item Created and oversaw presentation of new user orientation to over
300 students.
\end{itemize}
\dates{2009\,--\,2010}
 Sun Lab Consultant (promoted 2010)
\begin{itemize}
\item Performed system maintenance and provided user support for
70-machine Linux computer lab.
\end{itemize}

\jobhead{2009}{Course Developer and TA, Accelerated Introduction to CS}
{Brown CS Dept}
\begin{itemize}
\item Assisted in planning and designing a syllabus for a new course.
\item Developed, tested, and deployed 8 student projects in Java and Racket
(PLT Scheme).
\end{itemize}

\jobhead{2008\,--\,2009}{Communications Exhibit Intern}{Museum of Science in
Boston}
\begin{itemize}
\item Designed and implemented Python backend for an interactive
communications technology exhibit.
\item Integrated exhibit sensors and motors via configurable RS-232
hardware-software interface.
\end{itemize}
} % END PAST JOBS

\end{jobs}

% \vspace{-1ex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\marginlabel{Education}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{jobs}
%\jobhead{2017}{University of California, Berkeley}{PhD Mathematics}
\jobhead{2011\,--\,2017}{PhD Mathematics}{University of California, Berkeley}
%
\begin{itemize}
%
\item Thesis: \emph{Quasi-Fuchsian surface subgroups of infinite covolume
	Kleinian groups}.

\item GPA: 3.92.

\archive{\item Supervisor: Ian Agol}
\end{itemize}

\jobhead{2007\,--\,2011}{ScB Mathematics}{Brown University}
%\jobhead{2011}{Brown University}{ScB Mathematics}
%
\begin{itemize}
%
\item \emph{Phi Beta Kappa, magna cum laude, department honors.}

\archive{
David Howell Premium (\$5000, 1 awarded/year)
}


\item GPA: 3.86. \ \ \ Math GPA: 4.00. \ \ \ CS GPA: 4.00.

\end{itemize}

\archive{
{\bf Selected CS courses:}
\item Operating Systems with Lab
\item Programming Languages
\item Algorithm Design and Analysis
\item Computational Complexity
}

\end{jobs}

\vspace{-1.5ex}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\marginlabel{Projects}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{0.6ex}

\noindent
%
Emulator/assembler for Knuth's MIX machine (C\verb!++!).
1970s Unix-like OS (C and x86 assembly).
Graph library for pseudo-Anosov conjugacy (Haskell).
Compiler for simplified Haskell subset (OCaml, incomplete).
%
\archive{ % PAST PROJECTS

\begin{jobs}

\projecthead{2014}{Haskell Compiler}

\noindent Haskell-to-LLVM compiler, using hand-written canonical LR(1) parser
generator. Lexing and parsing complete. Planned type inference, desugaring, and
LLVM code generation phases, still incomplete. OCaml.

\archive{
\projecthead{2013}{Bestvina--Handel Algorithm}

\noindent Library that used graph algorithms to
compute and display train track invariants of surface maps.
Built to solve pseudo-Anosov conjugacy complexity, a then-open
problem. Haskell.
}

\projecthead{2010\,--\,2011}{Operating System}

\noindent OS port from Xen platform to full hardware emulator to improve Brown
OS course.  New bootloader, scheduler, memory management, linker/loader,
interrupt handlers, and drivers. Improved student deploy time by 10x and
prevented platform crashes. C and x86 asm.

\end{jobs}

\projecthead{2013\,--}{SICP Student Tools} \\Language suite and test cases for
students to use with SICP (Abelson and Sussman). Racket.

\projecthead{2012}{Worksheet Generator}
\vspace{0.5ex}
\\Web app to automate math
worksheet/homework/quiz creation for instructors.
Had potential to save Berkeley math dept over 500 man-hours per
semester. Incomplete. Python.

} % END PAST PROJECTS

\vspace{0.6ex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\marginlabel{Languages}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{0.6ex}
\noindent
%
Python, SQL, C, C\verb!++!.
%
\noindent {\it Also familiar with}:
%
R, Pandas, NumPy, Scikit-learn, PyTorch,
%
Java, PHP, JavaScript,
%
OCaml, Haskell, Lisp,
%
Rust, Fortran, x86 asm,
%
operating systems,
%
distributed systems,
%
Hive, Presto, Spark.
%
\archive{React, GraphQL}
\archive{
%
Command line (including grep, awk, sed), Version control (git, hg).\\


\noindent \textit{Also familiar with:
%
PHP, JavaScript, C}\verb!++!\textit{, OCaml, Scheme, Rust, Fortran,
%
HTML, x86 Assembly,
%
R, Matlab, Tensorflow,
%
Hive, Presto, Thrift, Buck, GraphQL, React, XHP, JSX,
%
Linux (Ubuntu, Debian, Arch),
%
Microsoft Excel (pivot tables, vlookup, visualizations), Mathematica, \LaTeX.
%
}
%
%
}
\archive{ % MORE SKILLS
Issue tracking (Jira), Code review (ReviewBoard)
C\verb!++!, Matlab
\LaTeX

Ballroom / Latin dance (...)
} % END MORE SKILLS

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%  OLD SECTIONS  %%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\archive{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\marginlabel{Math Research}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{jobs}

{\bf\dates{2012\,--}
Current research, with Ian Agol}
\begin{itemize}
\item Studying various problems in 3-manifold topology. Currently working on
using hierarchies of Haken 3-manifolds to prove nontriviality of the
Reshetikhin--Turaev invariants on such manifolds.
\end{itemize}

{\bf \dates{2010 Sum.}
Langton's Ant, with
Richard Schwartz}
\begin{itemize}
\item Proved Turing-completeness of generalized Langton's Ant dynamical systems. 
\end{itemize}

{\bf\dates{2009 Sum.}
Norms on $\mathbb{R}^2$, with
Justin Peters}
\begin{itemize}
\item Proved results on extremal elements in symmetric convex subspaces of the
space of norms on $\mathbb{R}^2$.
\end{itemize}
\end{jobs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\marginlabel{Volunteer Work}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{jobs}
\dates{2012\,--}
	Organizer, Triple Rock graduate student seminar, UC Berkeley.
\dates{2012\,--}
	Social Coordinator, Berkeley Ballroom.
\dates{2011}
	Organizer, Many Cheerful Facts graduate student seminar, UC Berkeley.
\dates{2010\,--\,2011}
	Vice President, Mathematics Department Undergraduate
	Group, Brown University.
\dates{2010}
	Interim Coordinator, Symposium for Undergraduates in
	the Mathematical Sciences, Brown University.
\dates{2009\,--\,2010}
	Webmaster, Brown University Chorus.
\end{jobs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\marginlabel{Math Research}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{jobs}

{\bf\dates{2012\,--}
Current research, with Ian Agol}
\begin{itemize}

\item Studying various problems in 3-manifold topology. Currently working on
using hierarchies of Haken 3-manifolds to prove nontriviality of the
Reshetikhin--Turaev invariants on such manifolds.

\end{itemize}

{\bf \dates{2010 Summer}
Langton's Ant, with
Richard Schwartz}
\begin{itemize}
\item Studied the asymptotic and computational properties of the Langton's Ant
dynamical system, 
proved various entropic and measure-theoretic propositions, and 
obtained conjectures of ergodic behavior and periodic
point classification which can be generalized to related systems.
\end{itemize}

{\bf\dates{2009 Summer}
Norms on $\mathbb{R}^2$, with
Justin Peters}
\begin{itemize}
\item Researched the norms on $\mathbb{R}^2$ as a function space with intrinsic
properties, obtained multiple results concerning the extreme points and Choquet
integrals over extreme points in a symmetric subspace of the norm space, and
generalized these results to other symmetry groups and to higher dimensions.
\end{itemize}
\end{jobs}
%\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\marginlabel{Math Service}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{jobs}

\dates{2012\,--}
	Organizer, Triple Rock graduate student seminar, UC Berkeley.
\begin{itemize}
	\item Created website with Google Calendar backend to support
``floating-schedule'' seminar.
	\item Optimized the seminar format to improve speaker retention, talk
attendance, talk frequency, and audience committment.
\end{itemize}
\dates{2011}
	Organizer, Many Cheerful Facts graduate student seminar, UC Berkeley.
\begin{itemize}
	\item Found, vetted, and guided speakers for a low-pressure
introductory graduate student seminar.
\end{itemize}
\dates{2010\,--\,2011}
	Vice President, Mathematics Department Undergraduate
	Group, Brown University.
	%The math DUG, the most active DUG at
	%Brown, hosts multiple seminars and problem sessions each month
	%specifically targeted toward undergraduates in mathematics. We also
	%organize and host the annual Symposium for Undergraduates in the
	%Mathematical Sciences (SUMS).
\begin{itemize}
	\item Updated and maintained website for the math DUG.
	\item Helped organize and oversee seminars, problem sessions, and
panels.
\end{itemize}
\dates{2010}
	Interim Coordinator, Symposium for Undergraduates in
	the Mathematical Sciences, Brown University.
\begin{itemize}
	\item Stepped in to
	organize rooms, set up equipment, prepare handouts, register
	and direct attendees, and introduce student speakers at SUMS.
	\item
	Handled multiple unexpected scenarios when other organizers were
	unavailable.
\end{itemize}
\end{jobs}
}

\archive{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\marginlabel{References}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  
  \begin{tabular}{l@{\qquad}l}
  \begin{tabular}{l}
  Tom Doeppner \\
  Department of Computer Science \\
  Brown University \\
  Providence, RI 02912 \\
  {\tt twd@cs.brown.edu} \\
  \\
  Christopher Siden \\
  Delphix Corp. \\
  275 Middlefield Road, Suite 50 \\
  Menlo Park, CA 94025 \\
  {\tt csiden@delphix.com} \\
  \\
  \end{tabular}
   & 
  \begin{tabular}{l}
  Dorinda Moulton \\
  Department of Computer Science \\
  Brown University \\
  Providence, RI 02912 \\
  {\tt djm@cs.brown.edu} \\
  \\
  Ian Agol \\
  Department of Mathematics \\
  University of California, Berkeley \\
  Berkeley, CA 94720 \\
  {\tt ianagol@math.berkeley.edu} \\
  \\
  \end{tabular}
  \end{tabular}
 }
